Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [??? I changed PI to CI - change in supplementary accordingly; !!!fixed] featured at each resolution. The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50. The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.196 (SD=0.025) and 0.166 (SD=0.026) for the GM12878 and K562 cell lines, respectively [??? Add exact numbers, like $18.34 \pm 5.06 \%$ !!!added] (Supplementary Figure 3). The presence of class imbalance justifies the the need for using resampling techniques before predictive modeling.

[??? Very briefly introduce each technique, refer to Methods for details]

>>>>

Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [??? I changed PI to CI - change in supplementary accordingly; !!!fixed] featured at each resolution. The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50. The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.196 (SD=0.025) and 0.166 (SD=0.026) for the GM12878 and K562 cell lines, respectively [??? Add exact numbers, like $18.34 \pm 5.06 \%$ !!!added] (Supplementary Figure 3). To account for such imbalance we evaluated 4 re-sampling techniques (in addition to no re-sampling) before predicting TAD boundaries. **Random over-sampling** (ROS) was defined as sampling with replacement from TAD boundary regions. **Random under-sampling** (RUS) was defined as sampling with replacement from non-TAD boundary regions. Lastly, we considered **Synthetic minority over-sampling technique** (SMOTE), which is a combination of both random over- and under-sampling [@chawla2002smote].

[??? Very briefly introduce each technique, refer to Methods for details; !!!added]
